\bibliographystyle{alpha}
\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem{QRSComplexWiki}
QRS Complex,
\newblock \texttt{https://en.wikipedia.org/wiki/QRS\_complex} .
\newblock Stan na: 05.12.2015 r.

\bibitem{Augustyniak}
Augustyniak, P.
\newblock{\em Przetwarzanie sygnałów elektrodiagnostycznych}.
\newblock Uczelniane Wydawnictwo Naukowo - Dydaktyczne, AGH, Kraków, 2001 r.


\bibitem{RaportKoncowy}
Studenci Automatyki i Robotyki.
\newblock{\em ESDMiT - Raport końcowy}.
\newblock 04.02.2015 r.

\bibitem{KMeans}
MacQueen, J.
\newblock{\em Some methods for classification and analysis of multivariate observations}.
\newblock W materiałach: "Fifth Berkeley Symposium on Mathematical Statistics and Probability, Volume 1: Statistics", strony 281-297,
\newblock University of California Press, Berkeley, Kalifornia, USA, 1967. 

\bibitem{GMeans}
Hamerly, G., Elkan, Ch.
\newblock{\em{Learning the k in k-means}}.
\newblock W: Neural Information Processing Systems,
\newblock MIT Press, 2003.

\bibitem{GMeansExplanation}
Użytkownik 'ashenfad'.
\newblock{\em Divining the 'K' in K-means Clustering}.
\newblock \texttt{http://blog.bigml.com/2015\\/02/24/divining-the-k-in-k-means-clustering/}. 
\newblock Dodane: 24.02.2015 r.
\newblock Stan na: 05.12. 2015 r.

\bibitem{SVMWiki}
Support vector machine,
\newblock \texttt{https://en.wikipedia.org/wiki/Support\_vector\_machine} .
\newblock Stan na: 05.12.2015 r.

\bibitem{MITDB}
MIT-BIH Arrhythmia Database,
\newblock \texttt{https://www.physionet.org/physiobank/database/mitdb/}
\newblock Stan na: 05.12.2015 r.

\bibitem{SVMBasedArrhythmiaClassification}
Song, M. H., i inni.
\newblock{\em Support Vector Machine Based Arrhythmia Classification Using Reduced Features}.
\newblock International Journal of Control, Automation, and Systems, vol. 3, nr 4, strony 571-579, grudzień 2005.

\bibitem{Abhishek}
Thakare, A. S.
\newblock{\em QRS Complex Detection and Arrhythmia Classification}.
\newblock Uniwersytet Pune, Indie.

\bibitem{Laguna}
Laguna, P., Jane, R., Caminal, P.
\newblock{\em Adaptive Feature Extraction for QRS Classification and Ectopic Beat Detection}.
\newblock Computers in Cardiology, IEEE, 1991.

\bibitem{Moreas}
Moraes, J.C.T.B., Seixas, M.O., Vilani, F.N., Costa, E.V.
\newblock{\em A Real Time QRS Complex Classification Method using Mahalanobis Distance}.
\newblock Escola Politécnica da Universidade de São Paulo, São Paulo, Brazylia.

\end{thebibliography}